\Title

### 2016-03-20 manuscript/manuscript.tex
Corrections to SAm data sections by Val
Not included the model discussion

The seismic point estimates of Moho depth used in the cross-validation
procedure are from the data set of \citet{assumpcao2013a}.
The 937 data points in this data set are shown in Fig.~\ref{fig:sam-data}b.

@@

We split the sediment-free gravity data into the training and testing data
sets.
The training data set is a regular grid with $0.4^\circ$ grid spacing
(twice the spacing of the original data grid)
and $N_{lat} \times N_{lon} = 201 \times 151$ grid points,
a total of 30,351 observations.
The remaining 90,350 points compose the testing data set.
We test 16 values of the regularization parameter ($\mu$)
equally spaced on a logarithmic scale between $10^{-10}$ and $10^{-2}$.
Fig.~\ref{fig:sam-cv}a shows the Mean Square Error (MSE)
as a function of $\mu$.
The minimum MSE is found at $\mu = 10^{-10}$, the lowest value of $\mu$ tested,
suggesting that little or no regularization is required.

We proceed with the second cross-validation using $\mu = 10^{-10}$ in all
inversions.
We test all combinations of
seven values of $z_{ref}$, from 20 to 35 km with 2.5 km intervals,
and seven values of $\Delta\rho$, from 200 to 500 $kg/m^3$
with 50 $kg/m^3$ intervals.
Fig.~\ref{fig:sam-cv}b shows a map of the MSE
with respect to the \citet{assumpcao2013a} data set.
The MSE has a well defined minimum, indicated by the red triangle,
at $z_{ref} = 35\ km$ and $\Delta\rho = 400\ kg/m^3$.

>>>>

Fig.~\ref{fig:sam-data}b shows the 937 known Moho depths (colored dots) which
were estimated from seismological data by \citet{assumpcao2013a}.
This data set is used in the cross-validation procedure.

@@

We split the sediment-free gravity disturbance (Fig.~\ref{fig:sam-data}a) into
the training and testing data sets.
The training data set is a regular grid with $0.4^\circ$ grid spacing
(twice the spacing of the original data grid)
and $N_{lat} \times N_{lon} = 201 \times 151$ grid points,
a total of 30,351 observations.
The remaining 90,350 points compose the testing data set.
We test 16 values of the regularization parameter ($\mu$)
equally spaced on a logarithmic scale between $10^{-10}$ and $10^{-2}$.
Fig.~\ref{fig:sam-cv}a shows the Mean Square Error (MSE)
as a function of $\mu$.
The minimum MSE is found at $\mu = 10^{-10}$, the lowest value of $\mu$ tested,
suggesting that little or no regularization is required.

We proceed with the second cross-validation using $\mu = 10^{-10}$ in all
inversions.
We test all combinations of
seven values of $z_{ref}$, from 20 to 40 km with 2.5 km intervals,
and seven values of $\Delta\rho$, from 200 to 500 $kg/m^3$
with 50 $kg/m^3$ intervals.
Fig.~\ref{fig:sam-cv}b shows a map of the MSE
with respect to the \citet{assumpcao2013a} data set.
The MSE has a well-defined minimum, indicated by the red triangle,
at $z_{ref} = 35\ km$ and $\Delta\rho = 400\ kg/m^3$.
